### 2018-11-27 README.Rmd
rebuild docs

---
output:
  md_document:
    variant: gfm
---

[![Build Status](https://travis-ci.org/cboettig/eml2.svg?branch=master)](https://travis-ci.org/cboettig/eml2)
[![Coverage Status](https://img.shields.io/codecov/c/github/cboettig/eml2/master.svg)](https://codecov.io/github/cboettig/eml2?branch=master)
[![stability-experimental](https://img.shields.io/badge/stability-experimental-orange.svg)](https://github.com/joethorley/stability-badges#experimental)

@@

# eml2

The goal of `eml2` is to provide both a drop-in replacement for the higher-level functions of the existing EML package while also providing additional functionality.

`eml2` uses only simple and familiar list structures (S3 classes) instead of the more cumbersome use of S4 found in the original EML.  While the higher-level functions are identical, this makes it easier to for most users and developers to work with `eml` objects and also to write their own functions for creating and manipulating EML objects.  Under the hood, `eml2` relies on the [emld](https://github.com/cboettig/emld) package, which uses a Linked Data representation for EML.  It is this approach which lets us combine the simplicity of lists with the specificy required by the XML schema.

@@

```{r message=FALSE, warning=FALSE}
library(eml2)
```

@@

Here we show a the creation of a relatively complete EML document using `eml2`.  This closely parallels the function calls shown in the original EML [R-package vignette](https://ropensci.github.io/EML/articles/creating-EML.html).

@@

The original EML R package defines a set of higher-level `set_*` methods to facilitate the creation of complex metadata structures.  `eml2` provides these same methods, taking the same arguments for `set_coverage`, `set_attributes`, `set_physical`, `set_methods` and `set_textType`, as illustrated here:

@@

```{r}
attributes <- read.table(system.file("extdata/hf205_attributes.csv", package = "eml2"))
factors <- read.table(system.file("extdata/hf205_factors.csv", package = "eml2"))
attributeList <- 
  set_attributes(attributes, 
                 factors, 
                 col_classes = c("character", 
                                 "Date",
                                 "Date",
                                 "Date",
                                 "factor",
                                 "factor",
                                 "factor",
                                 "numeric"))
```

>>>>

---
output: github_document
---

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)
[![Windows build status](https://ci.appveyor.com/api/projects/status/u2gw24yfkvxgny96?svg=true)](https://ci.appveyor.com/project/cboettig/eml)
[![codecov](https://codecov.io/gh/ropensci/EML/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/EML)
[![CRAN status](https://www.r-pkg.org/badges/version/EML)](https://cran.r-project.org/package=EML)

@@

# EML

The goal of `EML` is to provide both a drop-in replacement for the higher-level functions of the existing EML package while also providing additional functionality.

`EML` uses only simple and familiar list structures (S3 classes) instead of the more cumbersome use of S4 found in the original EML.  While the higher-level functions are identical, this makes it easier to for most users and developers to work with `eml` objects and also to write their own functions for creating and manipulating EML objects.  Under the hood, `EML` relies on the [emld](https://github.com/cboettig/emld) package, which uses a Linked Data representation for EML.  It is this approach which lets us combine the simplicity of lists with the specificy required by the XML schema.

@@

```{r message=FALSE, warning=FALSE}
library(EML)
```

@@

Here we show a the creation of a relatively complete EML document using `EML`.  This closely parallels the function calls shown in the original EML [R-package vignette](https://ropensci.github.io/EML/articles/creating-EML.html).

@@

The original EML R package defines a set of higher-level `set_*` methods to facilitate the creation of complex metadata structures.  `EML` provides these same methods, taking the same arguments for `set_coverage`, `set_attributes`, `set_physical`, `set_methods` and `set_textType`, as illustrated here:

@@

```{r}
attributes <- read.table(system.file("extdata/hf205_attributes.csv", package = "EML"))
factors <- read.table(system.file("extdata/hf205_factors.csv", package = "EML"))
attributeList <- 
  set_attributes(attributes, 
                 factors, 
                 col_classes = c("character", 
                                 "Date",
                                 "Date",
                                 "Date",
                                 "factor",
                                 "factor",
                                 "factor",
                                 "numeric"))
```
